BioTime

### 2019-04-11 biotime.Rmd
merge data.

Start with trying to merge bird data via taxadb
```{r}
library(taxadb)

@@

##Counts show that OTT is the best authority for both data sets
get_match_counts(data %>% filter(taxa == "Birds"), "genus_species")
get_match_counts(bird_trait, "scientific")

Merge functional traits on OTT ids
```{r}
#Getting matches by scientific name 
bird_data <- data %>% 
  filter(taxa == "Birds") %>%
  select(genus_species) %>%
  drop_na() %>%
  distinct() %>%
  mutate(id = get_ids(genus_species, "ott")) %>%
  left_join(data, by = "genus_species")

bird_common <- bird_data %>%
  filter(is.na(id)) %>%
  select(genus_species) %>%
  distinct() %>%
  by_rank("Aves", "class", "ott")

sci_names <- by_name(data$genus_species, "ott")

comm_names <- by_common(data$genus, "ott")
```

>>>>

Check which authority would result in the most matches 
```{r}
library(taxadb)

@@

##Counts show that OTT is the best authority for both data sets
get_match_counts(data %>% filter(taxa == "Birds"), "genus_species")
get_match_counts(data, "genus_species")
get_match_counts(bird_trait, "scientific")
get_match_counts(mamm_trait, "scientific")
```

OTT is the best authority but doesn't have common names, so we use the next best ITIS
```{r}
#Getting matches by scientific name 
biotime <- data %>% 
  #filter(taxa == "Birds") %>%
  select(genus_species) %>%
  drop_na() %>%
  distinct() %>%
  mutate(id = get_ids(genus_species, "itis")) %>%
  left_join(data, by = "genus_species")

#Getting matches by sci name and common name 
biotime_ids <- by_name(unique(data$genus_species), "itis") %>%
  bind_rows(by_common(unique(data$genus_species), "itis")) %>%
  drop_na(acceptedNameUsageID)

#There is not a unique taxonID for each species, different pop's have different ID's for some marine mammals
#Names with more than one match that need to be resolved manually
#biotime_ids %>% group_by(sort) %>% filter(n()>1) %>% View()

biotime_data <- biotime_ids %>%
  group_by(sort) %>%
  filter(n() < 2) %>%
  ungroup(sort) %>%
  select(taxonID,input) %>%
  left_join(data, by = c("input" = "genus_species"))
```
